---
title: "Data Programming"
subtitle: "Homework 2"
author: "Lucas Lorenzo Jakin"
date: "`r format(Sys.time(), '%e %B %Y')`"
format: 
  html:
    embed-resources: true
execute: 
  warning: false
  messages: false
  echo: true
  error: true
---

## Solutions

Submit a **.html** file created using Quarto via e-classroom. A sample is attached. Display all code (packages,input) and output.



Import the csv file from **https://www.kaggle.com/datasets/vishnuvarthanrao/windows-store** (login is required). Parse the Date column into a date.

```{r}

```

Careful with dealing with missing/NA data at the end. Some functions like sum, min, max have a 
 option.
Answer these questions independentlty:


1.  Display the dataframe as a tibble.
2.  How long has the data been collected?
3.  Among the highest rated apps return the 10 apps (rows) with the highest amount of reviews. Display only the first 3 columns.
4.  Show the number of apps created per month.
5.  Sort the rows of the dataframe from the least wordy to most wordy app name. Display the first 15.

```{r}
# solve 1-5 here
library(tidyverse)
#importing csv file
df <- read.csv("msft.csv")
as.tibble(df)
#1 Display the dataframe as a tibble
# Parse Date column into a date
df$Date <- dmy(df$Date)
as.tibble(df)

#2 How long has the data been collected?
diff_date <- max(df$Date, na.rm=T) - min(df$Date, na.rm=T)
print(diff_date)

#3 10 rows with highest amount of reviews. Display only first 3 columns
highest_rated <- df[df$Rating==5,]
highest_rated <- highest_rated[order(highest_rated$No.of.people.Rated, decreasing = T),]
highest_rated <- highest_rated[1:10, 1:3]
highest_rated

#4 Show number of apps created per month
appsPerMonth <- table(format(df$Date, "%m"), useNA="always")
appsPerMonth
#df %>% mutate(month = format(df$Date, "%m")) %>% count(month) %>% unname()

#5 Sort rows of dataframe from least wordy to most wordy app name.
# Displaye first 15
library(dplyr)
df %>% arrange(nchar(Name)) %>% head(15)
```

```{r}
#| echo: false
#installs tidyverse and quarto if not done already, delete this chunk after running it once.
normalpackages<-c("tidyverse","quarto")
   new.packages <- normalpackages[!(normalpackages %in% installed.packages()[,"Package"])]
  if(length(new.packages)>0) {install.packages(new.packages,dependencies =T,quiet = T)}
```

