---
title: "Data Programming"
subtitle: "Homework 3"
author: "Lucas Lorenzo Jakin"
date: "`r format(Sys.time(), '%e %B %Y')`"
format: 
  html:
    embed-resources: true
execute: 
  warning: false
  messages: false
  echo: true
  error: true
---

## Solutions

Submit a **.html** file created using Quarto via e-classroom. A sample is attached. Display all code (packages,input) and output.


### 1

Draw a line chart with ggplot of temperature over time side by side for the 2 build-in data frames **beaver1** and **beaver2**. Add a Title and units on the Y-axis for temperature.

```{r}
# Solve 1 here!
```

### 2

You are given the worth of 1 EUR in some currencies.
```{r}
c(EUR=1, datasets::euro)
```

Write a function of two parameters:

  1. a named numeric vector, with values representing the amount of currency in the corresponding name owned,
  2. (optional) a currency to convert to.
  
The function returns the total amount from 1. as the currency specified in 2. If currency in 2. is not specified then return the value in EUR. If a currency from 1. does not exists, then that part of the vector contributes 0 to the output. If the currency from 2. does not exist then return 0.

```{r}
# Solve 2 here (Enter the function)
```


```{r}
#| echo: false
#installs tidyverse and quarto if not done already, delete this chunk after running it once.
normalpackages<-c("tidyverse","quarto")
   new.packages <- normalpackages[!(normalpackages %in% installed.packages()[,"Package"])]
  if(length(new.packages)>0) {install.packages(new.packages,dependencies =T,quiet = T)}
```

