---
title: "Data Programming"
subtitle: "Homework 3"
author: "Lucas Lorenzo Jakin"
date: "`r format(Sys.time(), '%e %B %Y')`"
format: 
  html:
    embed-resources: true
execute: 
  warning: false
  messages: false
  echo: true
  error: true
---

## Solutions

Submit a **.html** file created using Quarto via e-classroom. A sample is attached. Display all code (packages,input) and output.


### 1

Draw a line chart with ggplot of temperature over time side by side for the 2 build-in data frames **beaver1** and **beaver2**. Add a Title and units on the Y-axis for temperature.

```{r}
# Solve 1 here!
library(tidyverse)
library(ggplot2)
# GGPLOT OF BEAVER 1!!!!!!!!!!!!!!!!!!!!!!
temp1 <- beaver1 # !!!!
# day to date format
beaverMonth <- as.Date(temp1$day, format ="%B %d")
beaverMonth2 <- format(beaverMonth, "%b %d")
temp1$dateTime <- beaverMonth2 
# time to POSIX format
beaverT <- sprintf("%04d", as.numeric(temp1$time))
beaverTime <- format(strptime(beaverT,"%H%M"), "%H:%M")
temp1$hmin <- beaverTime
temp1$dayAndTime <- paste(temp1$dateTime,temp1$hmin)
dftemp1 <- data.frame(datetime1 = as.POSIXct(temp1$dayAndTime, format = "%b %d %H:%M"), sprem1 = temp1$temp)

ggplot(dftemp1,aes(x=datetime1, y = sprem1)) + geom_path(color="red") +
  scale_x_datetime(date_breaks = "6 hour",date_labels = "%b %d %H:%M") +
  labs(y="Temperature (°C)", title = "Temperature of beavers over time") + theme_minimal()



#GGPLOT OF BEAVER2!!!!!!!!!!!!!!!
temp2 <- beaver2
beaverMonthTwo <- as.Date(temp2$day, format ="%B %d")
beaverMonth2Two <- format(beaverMonthTwo, "%b %d")
temp2$dateTime <- beaverMonth2Two 
# time to POSIX format
beaverT2 <- sprintf("%04d", as.numeric(temp2$time))
beaverTime2 <- format(strptime(beaverT2,"%H%M"), "%H:%M")
temp2$hmin <- beaverTime2
temp2$dayAndTime <- paste(temp2$dateTime,temp2$hmin)
dftemp2 <- data.frame(datetime2 = as.POSIXct(temp2$dayAndTime, format = "%b %d %H:%M"), sprem2 = temp2$temp)

ggplot(dftemp2,aes(x=datetime2, y = sprem2)) + geom_path(color="lightblue") +
  scale_x_datetime(date_breaks = "6 hour",date_labels = "%b %d %H:%M") +
  labs(y="Temperature (°C)", title = "Temperature of beavers over time") + theme_minimal()

```

### 2

You are given the worth of 1 EUR in some currencies.
```{r}
c(EUR=1, datasets::euro)
```

Write a function of two parameters:

  1. a named numeric vector, with values representing the amount of currency in the corresponding name owned,
  2. (optional) a currency to convert to.
  
The function returns the total amount from 1. as the currency specified in 2. If currency in 2. is not specified then return the value in EUR. If a currency from 1. does not exists, then that part of the vector contributes 0 to the output. If the currency from 2. does not exist then return 0.

```{r}
# Solve 2 here (Enter the function)

convert.all <- function(amount, currency = "EUR"){
  # Define conversion rates
  currencies <- c(EUR = 1, datasets::euro)
  # if currency doesn't exist return 0
  if (!(currency %in% names(currencies))){
    return(0)
  }
  converted_values <- amount / currencies[names(amount)]
  sum_amount <- sum(converted_values, na.rm=T) # na.rm for taking care of NA values (if currency don't exist then +0)
  return (sum_amount * currencies[currency])
}

convert.all(c(EUR=6.5))
convert.all(c(EUR=3,ATS=2))
convert.all(c(EUR=3,EUR=2))
convert.all(c(EUR=3,DEM=2,SIT=10000))
convert.all(c(EUR=3,DEM=2,SIT=10000),"EUR")
convert.all(c(EUR=3,SIT=10000,DEM=2),"ESP")
convert.all(c(EUR=3,DEM=2,LIRA=100),"SIT")
```


```{r}
#| echo: false
#installs tidyverse and quarto if not done already, delete this chunk after running it once.
normalpackages<-c("tidyverse","quarto")
   new.packages <- normalpackages[!(normalpackages %in% installed.packages()[,"Package"])]
  if(length(new.packages)>0) {install.packages(new.packages,dependencies =T,quiet = T)}
```

